Abstractions for Multi-Sorted Substitutions

### 2024-03-11 paper/paper.tex
Update.

  Similar as for the \ACode{\ACon{Kit}}, we derive further definitions
  from the axioms of a \ACode{\ACon{CKit}}:
  \begin{itemize}
  \item
    We define map composition as motivated by the previous subsection:
    \LibCode\KComposition
  \item
    We show that the \ACode{\AField{\_\&/⋯\_}} operator behaves like
    \ACode{\AField{\_\&\_}} when applied to variables:
    \LibCode\KCKitAp
    % \LibCode\KCKitApProof

    % The \ACode{\AField{`/id}} on the left side is from \ACode{K₁⊔K₂}, whereas
    % the \ACode{\AField{`/id}} on the right side is from \ACode{K₂}.
  \item
    We show that lifting \ACode{\AField{\_↑\_}} distributes over
    composition:
    \LibCode\KDistLiftCompose
    % \LibCode\KDistLiftComposeProof
  \end{itemize}
  To make it easier to explicitly specify a \ACode{\ACon{CKit}},
  we define the notation \ACode{ϕ₁ \ADef{·[} C \ADef{]} ϕ₂}
  to stand for \ACode{ϕ₁ \ADef{·ₖ} ϕ₂} for some
  \ACode{\ACon{CKit}} \ACode{C}.
  % \LibCode\KCKitNotation

  We then define the \ACode{\ACon{CTraversal}} structure,
  which provides the \ACode{\AField{⋯-fusion}} lemma for arbitrary
  \ACode{\ACon{CKit}}s:
  \LibCode\KCTraversal

  Similar as for the \ACode{\ACon{Traversal}}, we derive further
  definitions from the axiom of a \ACode{\ACon{CTraversal}}:
  \begin{itemize}
  \item 
    A map \ACode{ϕ} followed by a weakening is equivalent to a
    weakening followed by \ACode{ϕ} that has been lifted over the weakened
    variable:
    \LibCode\KCommLiftWeaken
    % \LibCode\KCommLiftWeakenProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the same
    statement for multiple map applications:
    \LibCode\KCommLiftWeakenTraverse
    % \LibCode\KCommLiftWeakenTraverseProof
  \item 
    A weakening followed by a singleton substitution cancel each other out:
    \LibCode\KWeakenCancelsSingle
    % \LibCode\KWeakenCancelsSingleProof
    By applying \ACode{\AField{⋯-fusion}} and \ACode{\AField{⋯-id}} to
    this lemma, we get the same statement for multiple map applications:
    \LibCode\KWeakenCancelsSingleTraverse
    % \LibCode\KWeakenCancelsSingleTraverseProof
  \item 
    A singleton map can be swapped with any map \ACode{ϕ}:
    \LibCode\KDistLiftSingle
    % \LibCode\KDistLiftSingleProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the
    same statement for multiple map applications:
    \LibCode\KDistLiftSingleTraverse
    % \LibCode\KDistLiftSingleTraverseProof
  \item 
    We define \ACode{\ACon{CKit}} instances for each of the four
    combinations between renamings and substitutions:
    \LibCode\KCKitInstances
    Interestingly, the \ACode{\ADef{Cₛ}} instance has another
    \ACode{\ADef{CKit}} parameter.
    This allows us to first use \ACode{\ADef{Cᵣ}} as an argument,
    which yields the \ACode{\ADef{CKit}} between substitutions
    and renamings, and then use this resulting \ACode{\ADef{CKit}}
    as an argument for the case with two substitutions.
    As shown below, Agda's instance resolution is up for the task:

>>>>

  Similar as for the \ACode{\ACon{Kit}}, we derive further definitions
  from the axioms of a \ACode{\ACon{CKit}}:
  \begin{itemize}
  \item
    We define map composition as motivated by the previous subsection:
    \LibCode\KComposition
  % \item
  %   We show that the \ACode{\AField{\_\&/⋯\_}} operator behaves like
  %   \ACode{\AField{\_\&\_}} when applied to variables:
  %   \LibCode\KCKitAp
  %   % \LibCode\KCKitApProof

  %   % The \ACode{\AField{`/id}} on the left side is from \ACode{K₁⊔K₂}, whereas
  %   % the \ACode{\AField{`/id}} on the right side is from \ACode{K₂}.
  \item
    We show that lifting \ACode{\AField{\_↑\_}} distributes over
    composition:
    \LibCode\KDistLiftCompose
    % \LibCode\KDistLiftComposeProof
  \end{itemize}
  To make it easier to explicitly specify a \ACode{\ACon{CKit}},
  we define the notation \ACode{ϕ₁ \ADef{·[} C \ADef{]} ϕ₂}
  to stand for \ACode{ϕ₁ \ADef{·ₖ} ϕ₂} for some
  \ACode{\ACon{CKit}} \ACode{C}.
  % \LibCode\KCKitNotation

  We then define a structure,
  which provides the \ACode{\AField{⋯-fusion}} lemma for arbitrary
  \ACode{\ACon{CKit}}s:
  \LibCode\KCTraversal

  Similar as for the \ACode{\ACon{Traversal}}, we derive further
  definitions from the axioms of a \ACode{\ACon{CTraversal}}:
  \begin{itemize}
  \item 
    A map \ACode{ϕ} followed by a weakening is equivalent to a
    weakening followed by \ACode{ϕ} that has been lifted over the weakened
    variable:
    \LibCode\KCommLiftWeaken
    % \LibCode\KCommLiftWeakenProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the same
    statement for multiple map applications:
    \LibCode\KCommLiftWeakenTraverse
    % \LibCode\KCommLiftWeakenTraverseProof
  \item 
    A weakening followed by a singleton substitution cancel each other out:
    \LibCode\KWeakenCancelsSingle
    % \LibCode\KWeakenCancelsSingleProof
    By applying \ACode{\AField{⋯-fusion}} and \ACode{\AField{⋯-id}} to
    this lemma, we get the same statement for multiple map applications:
    \LibCode\KWeakenCancelsSingleTraverse
    % \LibCode\KWeakenCancelsSingleTraverseProof
  \item 
    A singleton map can be swapped with any map \ACode{ϕ}:
    \LibCode\KDistLiftSingle
    % \LibCode\KDistLiftSingleProof
    By applying \ACode{\AField{⋯-fusion}} to this lemma, we get the
    same statement for multiple map applications:
    \LibCode\KDistLiftSingleTraverse
    % \LibCode\KDistLiftSingleTraverseProof
  \item 
    We define \ACode{\ACon{CKit}} instances for each of the four
    combinations between renamings and substitutions:
    \LibCode\KCKitInstances
    Interestingly, the \ACode{\ADef{Cₛ}} instance has another
    \ACode{\ADef{CKit}} parameter.
    This allows us to first use \ACode{\ADef{Cᵣ}} as an argument,
    which yields the \ACode{\ADef{CKit}} between substitutions
    and renamings, and then use this resulting \ACode{\ADef{CKit}}
    as an argument for the case with two substitutions.
    As shown below, Agda's instance resolution is up for the task:
